---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Unzip the file, load it.


```{r, echo=TRUE}
unzip(zipfile="activity.zip")
df<-read.csv2("activity.csv",sep="," )
```
Change the data type for date 
```{r, echo=TRUE}
df$date<-as.Date(df$date,format="%Y-%m-%d")

```


## What is mean total number of steps taken per day?

Aggregate date by date
```{r, echo=TRUE}
df.date<-aggregate(df[1],list(df$date),sum)
colnames(df.date)<-c('date','steps')
```

Draw Histogram 
```{r, echo=TRUE}
hist(df.date$steps, main = paste("Total Steps Each Day"), col="blue", xlab="Number of Steps")
```

Mean of steps by day
```{r, echo=TRUE}
mean(df.date$steps,na.rm=TRUE)
```

Median of steps by day
```{r, echo=TRUE}
median(df.date$steps,na.rm=TRUE)
```

## What is the average daily activity pattern?

Mean of steps by interval by days
```{r, echo=TRUE}
df.steps<-aggregate(df[1],list(df$interval),mean,na.rm=TRUE)
colnames(df.steps)<-c('interval','steps')
```

Plot the average daily activity
```{r, echo=TRUE}
plot(df.steps$interval,df.steps$steps,type='l', xlab="Interval", ylab="Number of Steps",main="Average Number of Steps per Day by Interval")
```

Which Interval is the maximum average of steps
```{r, echo=TRUE}
df.steps[which.max(df.steps$steps),]$interval
```

## Imputing missing values
Sorry, I do nothing here



## Are there differences in activity patterns between weekdays and weekends?

Determine if the date corresponding to a day of week or a week-end. 

I don't use the recommand function because I had a problem of location (I'm french and the day of week were in French !!). So, i used the POSIXlt function. 

```{r, echo=TRUE}
df$day_type<-ifelse(as.POSIXlt(df$date)$wday %in% c(0,6),'week-end','week_day')
df.steps2<-aggregate(df[1],list(df$interval,df$day_type),mean,na.rm=TRUE)
colnames(df.steps2)<-c('interval','day_type','steps')
```

Plot the two activities graphs
```{r, echo=TRUE}
library(lattice)
 xyplot(df.steps2$steps ~ df.steps2$interval|df.steps2$day_type, main="Average Steps per Day by Interval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")

```
